Representing Scenes as Light Fields for Real Time Rendering in Virtual Reality Display

### 2021-01-05 TOG/1-introduction.tex
v0.01: title, abstract, submission ID

Writing research documents, such as conference/journal/white papers, patent applications, grant proposals, and course reports, is a core activity for many poor souls including professors, researchers, engineers, and students.
Since we must do it one way or another, sooner or later, we might as well do it as happily and effectively as possible.
Here are my personal practices and experiences, which I have repeatedly shared with my collaborators and students throughout all these years\note{~to the point that I finally decided to write up to save the troubles}.

@@

Some people, including very successful ones, write papers only at the end of a project, like days if not hours prior to a submission deadline.
This almost always leads to total chaos and breakdown, unless you have other means to keep track and organize all the relevant pieces of information.

@@

\input{TOG/example_fig}

>>>>

Started from remote desktops and online videos, cloud-based computing has show unprecedented potential to reshape computer graphics pipeline by completely relieving end-user's computational workload thus device bulkiness. In recent years, we have observed growing interactive streaming services such as Google Stadia or NVIDIA Shield. 
However, these off-the-shelf services have only been deployed in less latency sensitive platforms such as TV-based game consoles, due to the inevitable latency (more than 100ms \footnote{\url{https://www.pcgamer.com/heres-how-stadias-input-lag-compares-to-native-pc-gaming/}}. Immersive medias, such as virtual and augmented realities, demand remarkably lower latency and higher fidelity/speed for sickness-free and natural experience. Due to the consequently massive spatial-temporal data volume, there is no solution for streaming frames from server to individual end users today.

@@

@@

\input{example_fig}
